---
title: "Polar Histogram DGP"
output: html_document
---

Clear 
```{r}
rm(list = ls())
```

Library
```{r}
library(grid)
library(png)
library(magick)
library(tidyverse)
library(dplyr)

#spatial
library(rgdal)
library(sp)
library(spdplyr)
library(raster)
library(terra)
library(sf)
library(rgeos)
```

# 1 Read Street Network (with labelled boundaries - DGP + Electorial)
```{r}
snet = readOGR("Data/snet_elec_dgp.mif", verbose = FALSE)
```

# 2 Divide Street Network by Boundaries (DGP)
```{r}
#get list of zones
snet.df = as.data.frame(snet)
zonelists = unique(snet.df$PLN_AREA_N)

#remove empty zone
zonelist = zonelists[zonelists != ""]
zonelist = zonelist[order(zonelist)]
zonelines = c()

for (zone in zonelist){
  entry = snet %>% filter(PLN_AREA_N == zone)
  zonelines = c(zonelines, entry)
}

#Print List of DGP Zones
zonelines
```

Processing: Matrix functions for Angle Calculation
```{r}
lengt = function(c){
  (((c[1,1]-c[1,2])^2) + ((c[2,1]-c[2,2])^2))^0.5
}
angle = function(c){
  x1 = c[1,1]
  x2 = c[2,1]
  y1 = c[1,2]
  y2 = c[2,2]
  atan2(x2-x1,y1-y2)
}
```

Processing: Compute Angles in Dataframe (,1 = x    ,2 = y)
```{r}
calculate = function(snet){
  #test 1 coordinate
  #snet@lines[[4655]]@Lines[[1]]@coords
  
  no.feat = nrow(as.data.frame(snet))
  len = c()
  ang = c()
  no = c(1:no.feat)
  
  for (i in 1:no.feat){
    z = snet@lines[[i]]@Lines[[1]]@coords
    len = c(len, lengt(z))
    
    #Change angle to b
    a = as.double(paste(angle(z)))
    a = ( (a * 180) / (pi) ) + 90
    if (a>360){
      a = a-360
    }
    if (a<0){
      a = -a
    }
    ang = c(ang, a)
  }
  
  df = data.frame(no,len,ang)
  #df %>% arrange(rev(ang))
  #df %>% arrange(ang)
  
  #mirror across
  df1 = df
  ang = sapply(df1$ang+180, function (x) ifelse(x>=355,x-360,x))
  df2 = data.frame(no,len,ang)
  df3 = rbind(df1,df2)
  
  #df3 %>% arrange(rev(ang))
  #df3 %>% arrange(ang)
  return(df3)
}
```

# 4 Compile Data and Process Angles for each Zone's Network
```{r}
alldata = data.frame()

for (i in 1:length(zonelines)){
  lines = zonelines[[i]]
  dataline = calculate(lines)
  dataline$name = zonelist[i]
  alldata = rbind(alldata,dataline)
}

```

# 5 Binning and Calculation of Basic Network Entropy Measures
```{r}
#break all data into bins
alldata$bin <- cut(alldata$ang, breaks = seq(0, 360, by = 10), labels = 0:35)

#create df to store metrics
metrics = data.frame(DGP = zonelist, Ho = NaN, Hw = NaN, phi = NaN)

for (x in 1:length(zonelist)){
  loc =  zonelist[x]

  #filter all data by zones
  e = alldata %>% filter(name == loc)
  
  #compute data
  total_street =  nrow(e)
  total_length = sum(e$len)
  Ho = 0
  Hw = 0 
  for (i in 0:35){
    #calculate PROPORTION of this orientation Ho
    P_o = nrow(e %>% filter(bin == i)) / total_street
    H_o = P_o * log(P_o)
    #replace NaN with 0 : bin is not occupied at all
    H_o = replace(H_o, is.na(H_o), 0)
    Ho = Ho - H_o
    
    #calculate PROPORTION of weighted orientation(by length)
    P_w = sum(e %>% filter(bin == i) %>% .$len) / total_length
    H_w = P_w * log(P_w)
    H_w = replace(H_w, is.na(H_w), 0)
    Hw = Hw - H_w
  }
  
  #input metrics
  metrics[x,]$Ho = Ho
  metrics[x,]$Hw = Hw
  Hmax = log(36)
  Hg = log(4)
  metrics[x,]$phi = 1 - ( (Ho - Hg)/ (Hmax - Hg) )^2
}

metrics %>% arrange(desc(phi))  #print entropy measures

order = metrics %>% arrange(desc(phi)) %>% .$DGP
```

Plot Function: Default (By Zone) Rose Diagram
```{r}
plotrose = function(df3){
  ggplot(df3, aes(x = ang)) +
  geom_histogram(breaks = ((0:36 - 0.5)/36 * 360), fill = 'lightblue', color= 'black', closed = "right") +
  scale_x_continuous(
    breaks = 0:3/4*360, 
    labels = c("N", "E", "S", "W")
    
    ) +
  coord_polar(start=-pi/36) +
    
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0(df3$name[1]," | ",nrow(df3)/2))
}

#plotrose(alldata%>%filter(name == order[1]))
```

Plot Function: (Singapore) Rose Diagram
```{r}
plotsg = function(df3){
  ggplot(df3, aes(x = ang)) +
  geom_histogram(breaks = ((0:36 - 0.5)/36 * 360), fill = 'lightblue', color= 'black', closed = "right") +
  scale_x_continuous(
    breaks = 0:3/4*360, 
    labels = c("N", "E", "S", "W")
    ) +
    
  coord_polar(start=-pi/36) +
    
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("SINGAPORE | ",nrow(df3)/2))
}
```

Plot Function: (Singapore) Rose Diagram without Ticks
```{r}
plotsg_wt = function(df3){
  ggplot(df3, aes(x = ang)) +
  geom_histogram(breaks = ((0:36 - 0.5)/36 * 360), fill = 'lightblue', color= 'black', closed = "right") +
  scale_x_continuous(
    breaks = 0:3/4*360, 
    labels = c("N", "E", "S", "W")
    ) +
    
    coord_polar(start=-pi/36) +
    
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("SINGAPORE | ",nrow(df3)/2))
}

```

Function: Empty Rose Diagram
```{r}
plot_empty = function(df3){
  ggplot(df3, aes(x = ang)) +
    geom_histogram(binwidth = 10, boundary = 0, fill = 'lightblue', color= 'black', closed = "right") +
    scale_x_continuous(breaks=seq(0,360,90), limits=c(0,360)) +
    coord_polar(theta="x", start=3*pi/2, direction=-1) +
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("NORTH-EASTERN ISLANDS | ",nrow(df3)/2))
}

#plot_empty(alldata%>%filter(name == zonelist[55]))
```

# 6 Compute All Plots

By Entropy
```{r}
library(ggpubr)

p1 = plotrose(alldata%>%filter(name == order[1]))
p2 = plotrose(alldata%>%filter(name == order[2]))
p3 = plotrose(alldata%>%filter(name == order[3]))
p4 = plotrose(alldata%>%filter(name == order[4]))
p5 = plotrose(alldata%>%filter(name == order[5]))
p6 = plotrose(alldata%>%filter(name == order[6]))
p7 = plotrose(alldata%>%filter(name == order[7]))
p8 = plotrose(alldata%>%filter(name == order[8]))
p9 = plotrose(alldata%>%filter(name == order[9]))
p10 = plotrose(alldata%>%filter(name == order[10]))

p11 = plotrose(alldata%>%filter(name == order[11]))
p12 = plotrose(alldata%>%filter(name == order[12]))
p13 = plotrose(alldata%>%filter(name == order[13]))
p14 = plotrose(alldata%>%filter(name == order[14]))
p15 = plotrose(alldata%>%filter(name == order[15]))
p16 = plotrose(alldata%>%filter(name == order[16]))
p17 = plotrose(alldata%>%filter(name == order[17]))
p18 = plotrose(alldata%>%filter(name == order[18]))
p19 = plotrose(alldata%>%filter(name == order[19]))
p20 = plotrose(alldata%>%filter(name == order[20]))

p21 = plotrose(alldata%>%filter(name == order[21]))
p22 = plotrose(alldata%>%filter(name == order[22]))
p23 = plotrose(alldata%>%filter(name == order[23]))
p24 = plotrose(alldata%>%filter(name == order[24]))
p25 = plotrose(alldata%>%filter(name == order[25]))
p26 = plotrose(alldata%>%filter(name == order[26]))
p27 = plotrose(alldata%>%filter(name == order[27]))
p28 = plotrose(alldata%>%filter(name == order[28]))
p29 = plotrose(alldata%>%filter(name == order[29]))
p30 = plotrose(alldata%>%filter(name == order[30]))

p31 = plotrose(alldata%>%filter(name == order[31]))
p32 = plotrose(alldata%>%filter(name == order[32]))
p33 = plotrose(alldata%>%filter(name == order[33]))
p34 = plotrose(alldata%>%filter(name == order[34]))
p35 = plotrose(alldata%>%filter(name == order[35]))
p36 = plotrose(alldata%>%filter(name == order[36]))
p37 = plotrose(alldata%>%filter(name == order[37]))
p38 = plotrose(alldata%>%filter(name == order[38]))
p39 = plotrose(alldata%>%filter(name == order[39]))
p40 = plotrose(alldata%>%filter(name == order[40]))

p41 = plotrose(alldata%>%filter(name == order[41]))
p42 = plotrose(alldata%>%filter(name == order[42]))
p43 = plotrose(alldata%>%filter(name == order[43]))
p44 = plotrose(alldata%>%filter(name == order[44]))
p45 = plotrose(alldata%>%filter(name == order[45]))
p46 = plotrose(alldata%>%filter(name == order[46]))
p47 = plotrose(alldata%>%filter(name == order[47]))
p48 = plotrose(alldata%>%filter(name == order[48]))
p49 = plotrose(alldata%>%filter(name == order[49]))
p50 = plotrose(alldata%>%filter(name == order[50]))

p51 = plotrose(alldata%>%filter(name == order[51]))
p52 = plotrose(alldata%>%filter(name == order[52]))
p53 = plotrose(alldata%>%filter(name == order[53]))
p54 = plotrose(alldata%>%filter(name == order[54]))

p55 = plotsg(alldata) #Full Singapore Model
p0 = plot_empty(alldata%>%filter(name == order[55])) #If Empty is needed

#Arranging Multiplot
g_entropy_hz = ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
          p11,p12,p13,p14,p15,p16,p17,p18,p19,p20,
          p21,p22,p23,p24,p25,p26,p27,p28,p29,p30,
          p31,p32,p33,p34,p35,p36,p37,p38,p39,p40,
          p41,p42,p43,p44,p45,p46,p47,p48,p49,p50,
          p51,p52,p53,p54,p55, nrow=5, ncol=11, align = "v")

g_entropy_vt = ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
          p11,p12,p13,p14,p15,p16,p17,p18,p19,p20,
          p21,p22,p23,p24,p25,p26,p27,p28,p29,p30,
          p31,p32,p33,p34,p35,p36,p37,p38,p39,p40,
          p41,p42,p43,p44,p45,p46,p47,p48,p49,p50,
          p51,p52,p53,p54,p55, nrow=11, ncol=5, align = "v")

```

By Name
```{r}
n1 = plotrose(alldata%>%filter(name == zonelist[1]))
n2 = plotrose(alldata%>%filter(name == zonelist[2]))
n3 = plotrose(alldata%>%filter(name == zonelist[3]))
n4 = plotrose(alldata%>%filter(name == zonelist[4]))
n5 = plotrose(alldata%>%filter(name == zonelist[5]))
n6 = plotrose(alldata%>%filter(name == zonelist[6]))
n7 = plotrose(alldata%>%filter(name == zonelist[7]))
n8 = plotrose(alldata%>%filter(name == zonelist[8]))
n9 = plotrose(alldata%>%filter(name == zonelist[9]))
n10 = plotrose(alldata%>%filter(name == zonelist[10]))

n11 = plotrose(alldata%>%filter(name == zonelist[11]))
n12 = plotrose(alldata%>%filter(name == zonelist[12]))
n13 = plotrose(alldata%>%filter(name == zonelist[13]))
n14 = plotrose(alldata%>%filter(name == zonelist[14]))
n15 = plotrose(alldata%>%filter(name == zonelist[15]))
n16 = plotrose(alldata%>%filter(name == zonelist[16]))
n17 = plotrose(alldata%>%filter(name == zonelist[17]))
n18 = plotrose(alldata%>%filter(name == zonelist[18]))
n19 = plotrose(alldata%>%filter(name == zonelist[19]))
n20 = plotrose(alldata%>%filter(name == zonelist[20]))

n21 = plotrose(alldata%>%filter(name == zonelist[21]))
n22 = plotrose(alldata%>%filter(name == zonelist[22]))
n23 = plotrose(alldata%>%filter(name == zonelist[23]))
n24 = plotrose(alldata%>%filter(name == zonelist[24]))
n25 = plotrose(alldata%>%filter(name == zonelist[25]))
n26 = plotrose(alldata%>%filter(name == zonelist[26]))
n27 = plotrose(alldata%>%filter(name == zonelist[27]))
n28 = plotrose(alldata%>%filter(name == zonelist[28]))
n29 = plotrose(alldata%>%filter(name == zonelist[29]))
n30 = plotrose(alldata%>%filter(name == zonelist[30]))

n31 = plotrose(alldata%>%filter(name == zonelist[31]))
n32 = plotrose(alldata%>%filter(name == zonelist[32]))
n33 = plotrose(alldata%>%filter(name == zonelist[33]))
n34 = plotrose(alldata%>%filter(name == zonelist[34]))
n35 = plotrose(alldata%>%filter(name == zonelist[35]))
n36 = plotrose(alldata%>%filter(name == zonelist[36]))
n37 = plotrose(alldata%>%filter(name == zonelist[37]))
n38 = plotrose(alldata%>%filter(name == zonelist[38]))
n39 = plotrose(alldata%>%filter(name == zonelist[39]))
n40 = plotrose(alldata%>%filter(name == zonelist[40]))

n41 = plotrose(alldata%>%filter(name == zonelist[41]))
n42 = plotrose(alldata%>%filter(name == zonelist[42]))
n43 = plotrose(alldata%>%filter(name == zonelist[43]))
n44 = plotrose(alldata%>%filter(name == zonelist[44]))
n45 = plotrose(alldata%>%filter(name == zonelist[45]))
n46 = plotrose(alldata%>%filter(name == zonelist[46]))
n47 = plotrose(alldata%>%filter(name == zonelist[47]))
n48 = plotrose(alldata%>%filter(name == zonelist[48]))
n49 = plotrose(alldata%>%filter(name == zonelist[49]))
n50 = plotrose(alldata%>%filter(name == zonelist[50]))

n51 = plotrose(alldata%>%filter(name == zonelist[51]))
n52 = plotrose(alldata%>%filter(name == zonelist[52]))
n53 = plotrose(alldata%>%filter(name == zonelist[53]))
n54 = plotrose(alldata%>%filter(name == zonelist[54]))

n55 = plotsg(alldata)
n0 = plot_empty(alldata%>%filter(name == zonelist[55]))


g_name_hz = ggarrange(n1,n2,n3,n4,n5,n6,n7,n8,n9,n10,
          n11,n12,n13,n14,n15,n16,n17,n18,n19,n20,
          n21,n22,n23,n24,n25,n26,n27,n28,n29,n30,
          n31,n32,n33,n34,n35,n36,n37,n38,n39,n40,
          n41,n42,n43,n44,n45,n46,n47,n48,n49,n50,
          n51,n52,n53,n54,n55, nrow=5, ncol=11, align = "v")

g_name_vt = ggarrange(n1,n2,n3,n4,n5,n6,n7,n8,n9,n10,
          n11,n12,n13,n14,n15,n16,n17,n18,n19,n20,
          n21,n22,n23,n24,n25,n26,n27,n28,n29,n30,
          n31,n32,n33,n34,n35,n36,n37,n38,n39,n40,
          n41,n42,n43,n44,n45,n46,n47,n48,n49,n50,
          n51,n52,n53,n54,n55, nrow=11, ncol=5, align = "v")

```

# 7 Generating TIFFs
```{r}
tiff(filename="OutputVisuals/byEntropy5x11.tiff", width=40, height=22.5, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
g_entropy_hz
dev.off()

tiff(filename="OutputVisuals/byEntropy11x5.tiff", width=19, height=40, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
g_entropy_vt
dev.off()

tiff(filename="OutputVisuals/byName5x11.tiff", width = 40, height=22.5, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  g_name_hz
dev.off()

tiff(filename="OutputVisuals/byName11x5.tiff", width = 19, height=40, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  g_name_vt
dev.off()
```

