---
title: "Untitled"
output: html_document
---

Clear 
```{r}
rm(list = ls())
```


```{r}
library(grid)
library(png)
library(magick)
library(tidyverse)
library(dplyr)

#spatial
library(rgdal)
library(sp)
library(spdplyr)
library(raster)
library(terra)
library(sf)
library(rgeos)
```


```{r}
#read network (elect boundaries)
snet = readOGR("snet (labelled zones)_final_Elec_DGP.mif", verbose = FALSE)


#read boundary
#bound = readOGR("boundary.mif", verbose = FALSE)

#plot test
#plot(bound)
#plot(snet,add= TRUE, col= "Red")
#--plot(snet)
```



#Break Singapore Map into PLots

```{r}
#get list of zones
snet.df = as.data.frame(snet)
zonelists = unique(snet.df$PLN_AREA_N)
zonelists

#remove empty zone
zonelist = zonelists[zonelists != ""]
zonelist = zonelist[order(zonelist)]
zonelines = c()

for (zone in zonelist){
  entry = snet %>% filter(PLN_AREA_N == zone)
  zonelines = c(zonelines, entry)
}

#zonelines
```



















Function: Matrix functions for Angle Calculation
```{r}
lengt = function(c){
  (((c[1,1]-c[1,2])^2) + ((c[2,1]-c[2,2])^2))^0.5
}
angle = function(c){
  x1 = c[1,1]
  x2 = c[2,1]
  y1 = c[1,2]
  y2 = c[2,2]
  atan2(x2-x1,y1-y2)
}
```

Function: Calculate Dataframe for Angles
,1 = x    ,2 = y
```{r}

calculate = function(snet){
  #test 1 coordinate
  #snet@lines[[4655]]@Lines[[1]]@coords
  
  no.feat = nrow(as.data.frame(snet))
  len = c()
  ang = c()
  no = c(1:no.feat)
  
  for (i in 1:no.feat){
    z = snet@lines[[i]]@Lines[[1]]@coords
    len = c(len, lengt(z))
    
    #Change angle to b
    a = as.double(paste(angle(z)))
    a = ( (a * 180) / (pi) ) + 90
    if (a>360){
      a = a-360
    }
    if (a<0){
      a = -a
    }
    ang = c(ang, a)
  }
  
  df = data.frame(no,len,ang)
  #df %>% arrange(rev(ang))
  #df %>% arrange(ang)
  
  
  #mirror across
  df1 = df
  ang = sapply(df1$ang+180, function (x) ifelse(x>=360,x-360,x))
  df2 = data.frame(no,len,ang)
  df3 = rbind(df1,df2)
  
  #df3 %>% arrange(rev(ang))
  #df3 %>% arrange(ang)
  return(df3)
}
```

Compile Data and Process Angles for each network
```{r}
alldata = data.frame()

for (i in 1:length(zonelines)){
  lines = zonelines[[i]]
  dataline = calculate(lines)
  dataline$name = zonelist[i]
  alldata = rbind(alldata,dataline)
}

#plotrose(calculate(zonelines[[16]]))
```


#Try to fix bins?







Function: Plot Rose Diagram
```{r}
plotrose = function(df3){
  ggplot(df3, aes(x = ang)) +
    geom_histogram(binwidth = 10, boundary = 0, fill = 'lightblue', color= 'black', closed = "right") +
    scale_x_continuous(breaks=seq(0,360,90), limits=c(0,360)) +
    coord_polar(theta="x", start=3*pi/2, direction=-1) +
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0(df3$name[1]," | ",nrow(df3)/2))
}
#df3
#plotrose(df3)
```

Function: Plot Singapore Rose Diagram
```{r}
plotsg = function(df3){
  ggplot(df3, aes(x = ang)) +
    geom_histogram(binwidth = 10, boundary = 0, fill = 'lightblue', color= 'black', closed = "right") +
    scale_x_continuous(breaks=seq(0,360,90), limits=c(0,360)) +
    coord_polar(theta="x", start=3*pi/2, direction=-1) +
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("SINGAPORE | ",nrow(df3)/2))
}
```

Function: Plot Singapore Rose Diagram (remove Singapore's tix)
```{r}
plotsgs = function(df3){
  ggplot(df3, aes(x = ang)) +
    geom_histogram(binwidth = 10, boundary = 0, fill = 'lightblue', color= 'black', closed = "right") +
    scale_x_continuous(breaks=seq(0,360,90), limits=c(0,360)) +
    coord_polar(theta="x", start=3*pi/2, direction=-1) +
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("SINGAPORE | ",nrow(df3)/2))
}

```

Function: Plot Singapore Rose Diagram (EMPTY PLOT)
```{r}
plot_empty = function(df3){
  ggplot(df3, aes(x = ang)) +
    geom_histogram(binwidth = 10, boundary = 0, fill = 'lightblue', color= 'black', closed = "right") +
    scale_x_continuous(breaks=seq(0,360,90), limits=c(0,360)) +
    coord_polar(theta="x", start=3*pi/2, direction=-1) +
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("NORTH-EASTERN ISLANDS | ",nrow(df3)/2))
}
plot_empty(alldata%>%filter(name == zonelist[55]))
```

Plot Everything
```{r}
library(ggpubr)

p1 = plotrose(alldata%>%filter(name == zonelist[1]))
p2 = plotrose(alldata%>%filter(name == zonelist[2]))
p3 = plotrose(alldata%>%filter(name == zonelist[3]))
p4 = plotrose(alldata%>%filter(name == zonelist[4]))
p5 = plotrose(alldata%>%filter(name == zonelist[5]))
p6 = plotrose(alldata%>%filter(name == zonelist[6]))
p7 = plotrose(alldata%>%filter(name == zonelist[7]))
p8 = plotrose(alldata%>%filter(name == zonelist[8]))
p9 = plotrose(alldata%>%filter(name == zonelist[9]))
p10 = plotrose(alldata%>%filter(name == zonelist[10]))

p11 = plotrose(alldata%>%filter(name == zonelist[11]))
p12 = plotrose(alldata%>%filter(name == zonelist[12]))
p13 = plotrose(alldata%>%filter(name == zonelist[13]))
p14 = plotrose(alldata%>%filter(name == zonelist[14]))
p15 = plotrose(alldata%>%filter(name == zonelist[15]))
p16 = plotrose(alldata%>%filter(name == zonelist[16]))
p17 = plotrose(alldata%>%filter(name == zonelist[17]))
p18 = plotrose(alldata%>%filter(name == zonelist[18]))
p19 = plotrose(alldata%>%filter(name == zonelist[19]))
p20 = plotrose(alldata%>%filter(name == zonelist[20]))

p21 = plotrose(alldata%>%filter(name == zonelist[21]))
p22 = plotrose(alldata%>%filter(name == zonelist[22]))
p23 = plotrose(alldata%>%filter(name == zonelist[23]))
p24 = plotrose(alldata%>%filter(name == zonelist[24]))
p25 = plotrose(alldata%>%filter(name == zonelist[25]))
p26 = plotrose(alldata%>%filter(name == zonelist[26]))

p26_5 = plot_empty(alldata%>%filter(name == zonelist[55]))

p27 = plotrose(alldata%>%filter(name == zonelist[27]))
p28 = plotrose(alldata%>%filter(name == zonelist[28]))
p29 = plotrose(alldata%>%filter(name == zonelist[29]))
p30 = plotrose(alldata%>%filter(name == zonelist[30]))

p31 = plotrose(alldata%>%filter(name == zonelist[31]))
p32 = plotrose(alldata%>%filter(name == zonelist[32]))
p33 = plotrose(alldata%>%filter(name == zonelist[33]))
p34 = plotrose(alldata%>%filter(name == zonelist[34]))
p35 = plotrose(alldata%>%filter(name == zonelist[35]))
p36 = plotrose(alldata%>%filter(name == zonelist[36]))
p37 = plotrose(alldata%>%filter(name == zonelist[37]))
p38 = plotrose(alldata%>%filter(name == zonelist[38]))
p39 = plotrose(alldata%>%filter(name == zonelist[39]))
p40 = plotrose(alldata%>%filter(name == zonelist[40]))

p41 = plotrose(alldata%>%filter(name == zonelist[41]))
p42 = plotrose(alldata%>%filter(name == zonelist[42]))
p43 = plotrose(alldata%>%filter(name == zonelist[43]))
p44 = plotrose(alldata%>%filter(name == zonelist[44]))
p45 = plotrose(alldata%>%filter(name == zonelist[45]))
p46 = plotrose(alldata%>%filter(name == zonelist[46]))
p47 = plotrose(alldata%>%filter(name == zonelist[47]))
p48 = plotrose(alldata%>%filter(name == zonelist[48]))
p49 = plotrose(alldata%>%filter(name == zonelist[49]))
p50 = plotrose(alldata%>%filter(name == zonelist[50]))

p51 = plotrose(alldata%>%filter(name == zonelist[51]))
p52 = plotrose(alldata%>%filter(name == zonelist[52]))
p53 = plotrose(alldata%>%filter(name == zonelist[53]))
p54 = plotrose(alldata%>%filter(name == zonelist[54]))

p56 = plotsg(alldata)
p56s = plotsgs(alldata)

#ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
#          p11,p12,p13,p14,p15,p16,p17,p18,p19,p10,
#          p21,p22,p23,p24,p25,p26,p27,p28, nrow=7, ncol=4, align = "v")

```

11x5 -> 8x4
```{r}
#GRAPH FILE

g = ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
          p11,p12,p13,p14,p15,p16,p17,p18,p19,p20,
          p21,p22,p23,p24,p25,p26, p26_5,p27,p28,p29,p30,
          p31,p32,p33,p34,p35,p36,p37,p38,p39,p40,
          p41,p42,p43,p44,p45,p46,p47,p48,p49,p50,
          p51,p52,p53,p54,p56, nrow=7, ncol=8, align = "v")


#------HIGHEST RES

#tiff(filename="25x25 (internal_highres).tiff", width=25, height=25, units="in",
#     pointsize=1.5, compression="lzw", bg="white", res=600,
#     restoreConsole=TRUE)
#  g
#dev.off()


#------INTERNAL CIRCULATION

tiff(filename="(internal) 30x28.tiff", width=30, height=28, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  g
dev.off()


tiff(filename="(internal) 30x28_water.tiff", width=30, height=28, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  g + annotate("text", x = Inf, y = -Inf, label = "©ryan-places_spaces",
            hjust=1.1, vjust=-1.1, col="darkgrey", cex=4,
            fontface = "bold", alpha = 0.8)
dev.off()

#------INTERNAL CIRCULATION

#tiff(filename="(internal) 12x27.tiff", width=12, height=27, units="in",
#     pointsize=5, compression="lzw", bg="white", res=600,
#     restoreConsole=TRUE)
#g
#dev.off()


#tiff(filename="(internal) 12x27_water.tiff", width=12, height=27, units="in",
#     pointsize=5, compression="lzw", bg="white", res=600,
#     restoreConsole=TRUE)
#g + annotate("text", x = Inf, y = -Inf, label = "©ryan-places_spaces",
#            hjust=1.1, vjust=-1.1, col="darkgrey", cex=4,
#            fontface = "bold", alpha = 0.8)
#dev.off()



#------External CIRCULATION

jpeg(filename="(public) 2100x2000_water.jpeg", width=2100, height=2000, units="px",
     pointsize=50, quality=100,bg="White",
     restoreConsole=TRUE)
g + annotate("text", x = Inf, y = -Inf, label = "©ryan-places_spaces",
            hjust=1.1, vjust=-1.1, col="darkgrey", cex=6,
            fontface = "bold", alpha = 0.8)
dev.off()


png(filename="(public) 2100x2000_water.png", width=2100, height=2000, units="px",
     pointsize=50,bg="White",
     restoreConsole=TRUE)
g + annotate("text", x = Inf, y = -Inf, label = "©ryan-places_spaces",
            hjust=1.05, vjust=-1, col="darkgray", cex=8,
            fontface = "bold", alpha = 0.8)
dev.off()


```

#Visuals for Mug
```{r}

m = ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
          p11,p12,p13,p14,p15,p16,p17,p18,p19,p20,
          p21,p22,p23,p24,p25,p26,p27,p28,p29,p30,
          p31,p32,p33,p34,p35,p36,p37,p38,p39,p40,
          p41,p42,p43,p44,p45,p46,p47,p48,p49,p50,
          p51,p52,p53,p54,p56, nrow=5, ncol=11, align = "v")

tiff(filename="(mugshot) 20x40_water.tiff", width = 40, height=20, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  m
dev.off()

```







laptop 16:9       3200	1800

```{r}

m = ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
          p11,p12,p13,p14,p15,p16,p17,p18,p19,p20,
          p21,p22,p23,p24,p25,p26,p27,p28,p29,p30,
          p31,p32,p33,p34,p35,p36,p37,p38,p39,p40,
          p41,p42,p43,p44,p45,p46,p47,p48,p49,p50,
          p51,p52,p53,p54,p56, nrow=5, ncol=11, align = "v")

tiff(filename="(laptop) 16x9_.tiff", width = 40, height=22.5, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  m
dev.off()

jpeg(filename="(laptop) 16x9_.jpeg", width=3200, height=1800, units="px",
     pointsize=50, quality=100,bg="White",
     restoreConsole=TRUE)
  m
dev.off()



```

ipad 4:3 2048 x 1536
54
```{r}

m = ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
          p11,p12,p13,p14,p15,p16,p17,p18,p19,p20,
          p21,p22,p23,p24,p25,p26,p27,p28,p29,p30,
          p31,p32,p33,p34,p35,p36,p37,p38,p39,p40,
          p41,p42,p43,p44,p45,p46,p47,p48,p49,p50,
          p51,p52,p53,p54, nrow=9, ncol=6, align = "v")

tiff(filename="(ipad) 4x3_.tiff", width = 30, height=40, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  m
dev.off()



jpeg(filename="(ipad) 4x3_.jpeg", width=1536, height=2048, units="px",
     pointsize=50, quality=100,bg="White",
     restoreConsole=TRUE)
  m
dev.off()

```

```{r}

```
