---
title: "Untitled"
output: html_document
---

#Spatial Configuration of Singapore's Street Networks

Street Networks support a wide range of urban processes

Likwise 

Geometric orientation

This data visualization 


Traffic Patterns and Travel Behaviour
Social Logic


This visualization was inspired by Geoff Boeing, where he conceptualized the use of a polar histogram to compare orientations of streets in cities around the works. The polar histogram charts out the frequencies of streets at different angles. For Instance, a cross (+) appearance would imply a grid-like street network structure. This methodology was recreated in R and applied it to street network data to analyze the difference in spatial configurations within the 55 planning boundaries in Singapore (MP19). The analysis accounts for a multi-modal street network and the number of line segments is shown on the number to the right of each name.

This analysis sought
This experiment, not only serves as an idea for me to think about, but also intends to capture the aesthetics of our local streets in a rather unorthodox form.


Clear 
```{r}
rm(list = ls())
```


```{r}
library(grid)
library(png)
library(magick)
library(tidyverse)
library(dplyr)

#spatial
library(rgdal)
library(sp)
library(spdplyr)
library(raster)
library(terra)
library(sf)
library(rgeos)
```


```{r}
#read network (elect boundaries)
snet = readOGR("snet (labelled zones)_final_Elec_DGP.mif", verbose = FALSE)


#read boundary
#bound = readOGR("boundary.mif", verbose = FALSE)

#plot test
#plot(bound)
#plot(snet,add= TRUE, col= "Red")
#--plot(snet)
```



#Break Singapore Map into PLots

```{r}
#get list of zones
snet.df = as.data.frame(snet)
zonelists = unique(snet.df$PLN_AREA_N)
zonelists

#remove empty zone
zonelist = zonelists[zonelists != ""]
zonelist = zonelist[order(zonelist)]
zonelines = c()

for (zone in zonelist){
  entry = snet %>% filter(PLN_AREA_N == zone)
  zonelines = c(zonelines, entry)
}

#zonelines
```



















Function: Matrix functions for Angle Calculation
```{r}
lengt = function(c){
  (((c[1,1]-c[1,2])^2) + ((c[2,1]-c[2,2])^2))^0.5
}
angle = function(c){
  x1 = c[1,1]
  x2 = c[2,1]
  y1 = c[1,2]
  y2 = c[2,2]
  atan2(x2-x1,y1-y2)
}
```

Function: Calculate Dataframe for Angles
,1 = x    ,2 = y
```{r}

calculate = function(snet){
  #test 1 coordinate
  #snet@lines[[4655]]@Lines[[1]]@coords
  
  no.feat = nrow(as.data.frame(snet))
  len = c()
  ang = c()
  no = c(1:no.feat)
  
  for (i in 1:no.feat){
    z = snet@lines[[i]]@Lines[[1]]@coords
    len = c(len, lengt(z))
    
    #Change angle to b
    a = as.double(paste(angle(z)))
    a = ( (a * 180) / (pi) ) + 90
    if (a>360){
      a = a-360
    }
    if (a<0){
      a = -a
    }
    ang = c(ang, a)
  }
  
  df = data.frame(no,len,ang)
  #df %>% arrange(rev(ang))
  #df %>% arrange(ang)
  
  
  #mirror across
  df1 = df
  ang = sapply(df1$ang+180, function (x) ifelse(x>=355,x-360,x))
  df2 = data.frame(no,len,ang)
  df3 = rbind(df1,df2)
  
  #df3 %>% arrange(rev(ang))
  #df3 %>% arrange(ang)
  return(df3)
}
```

Compile Data and Process Angles for each network
```{r}
alldata = data.frame()

for (i in 1:length(zonelines)){
  lines = zonelines[[i]]
  dataline = calculate(lines)
  dataline$name = zonelist[i]
  alldata = rbind(alldata,dataline)
}

#plotrose(calculate(zonelines[[16]]))
```

Binning and Calculations
```{r}
#e = alldata%>%filter(name == zonelist[1])%>% arrange(ang)

#break all data into bins
alldata$bin <- cut(alldata$ang, breaks = seq(0, 360, by = 10), labels = 0:35)

#create df to store metrics
metrics = data.frame(DGP = zonelist, Ho = NaN, Hw = NaN, phi = NaN)

for (x in 1:length(zonelist)){
  loc =  zonelist[x]

  #filter all data by zones
  e = alldata %>% filter(name == loc)
  
  #compute data
  total_street =  nrow(e)
  total_length = sum(e$len)
  
  print(paste0(loc,total_street))
  Ho = 0
  Hw = 0 
  for (i in 0:35){
    #calculate PROPORTION of this orientation Ho
    P_o = nrow(e %>% filter(bin == i)) / total_street
    H_o = P_o * log(P_o)
    #replace NaN with 0 : bin is not occupied at all
    H_o = replace(H_o, is.na(H_o), 0)
    Ho = Ho - H_o
    
    #calculate PROPORTION of weighted orientation(by length)
    P_w = sum(e %>% filter(bin == i) %>% .$len) / total_length
    H_w = P_w * log(P_w)
    H_w = replace(H_w, is.na(H_w), 0)
    Hw = Hw - H_w
  }
  
  #input metrics
  metrics[x,]$Ho = Ho
  metrics[x,]$Hw = Hw
  Hmax = log(36)
  Hg = log(4)
  metrics[x,]$phi = 1 - ( (Ho - Hg)/ (Hmax - Hg) )^2
}
metrics %>% arrange(desc(phi))
order = metrics %>% arrange(desc(phi)) %>% .$DGP

```

Function: Plot Rose Diagram
```{r}
plotrose = function(df3){
  ggplot(df3, aes(x = ang)) +
    geom_histogram(binwidth = 10, boundary = 0, fill = 'lightblue', color= 'black', closed = "right") +
    scale_x_continuous(breaks=seq(0,360,90), limits=c(0,360),
                       labels = c("","/N", "/W", "/S", "E")) +
    coord_polar(theta="x", start=3*pi/2, direction=-1) +
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0(df3$name[1]," | ",nrow(df3)/2))
}
seq(0,360,90)
plotrose(alldata%>%filter(name == order[50]))
```


Function: Plot Rose Diagram
```{r}
plotrose = function(df3){
  ggplot(df3, aes(x = ang)) +
  geom_histogram(breaks = ((0:36 - 0.5)/36 * 360), fill = 'lightblue', color= 'black', closed = "right") +
  scale_x_continuous(
    breaks = 0:3/4*360, 
    labels = c("N", "E", "S", "W")
    
    ) +
  coord_polar(start=-pi/36) +
    
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0(df3$name[1]," | ",nrow(df3)/2))
}

#plotrose(alldata%>%filter(name == order[1]))
```

Function: Plot Singapore Rose Diagram
```{r}
plotsg = function(df3){
  ggplot(df3, aes(x = ang)) +
  geom_histogram(breaks = ((0:36 - 0.5)/36 * 360), fill = 'lightblue', color= 'black', closed = "right") +
  scale_x_continuous(
    breaks = 0:3/4*360, 
    labels = c("N", "E", "S", "W")
    ) +
    
  coord_polar(start=-pi/36) +
    
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("SINGAPORE | ",nrow(df3)/2))
}

#plotsg(alldata)
```

Function: Plot Singapore Rose Diagram (remove Singapore's tix)
```{r}
plotsgs = function(df3){
  ggplot(df3, aes(x = ang)) +
  geom_histogram(breaks = ((0:36 - 0.5)/36 * 360), fill = 'lightblue', color= 'black', closed = "right") +
  scale_x_continuous(
    breaks = 0:3/4*360, 
    labels = c("N", "E", "S", "W")
    ) +
    
    coord_polar(start=-pi/36) +
    
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("SINGAPORE | ",nrow(df3)/2))
}

```

Function: Plot Singapore Rose Diagram (EMPTY PLOT)
```{r}
plot_empty = function(df3){
  ggplot(df3, aes(x = ang)) +
    geom_histogram(binwidth = 10, boundary = 0, fill = 'lightblue', color= 'black', closed = "right") +
    scale_x_continuous(breaks=seq(0,360,90), limits=c(0,360)) +
    coord_polar(theta="x", start=3*pi/2, direction=-1) +
    xlab(NULL)+ylab(NULL) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    #theme_bw()
    
     theme(axis.text = element_text(size = rel(0.7)),
           axis.ticks = element_line(colour = "black"),
           legend.key = element_rect(colour = "grey80"),
           panel.background = element_rect(fill = "white", colour = NA),
           panel.border = element_rect(fill = NA, colour = "grey50"),
           panel.grid.major = element_line(colour = "grey90", size = 0.2),
           panel.grid.minor = element_line(colour = "grey98", size = 0.5),
           strip.background = element_rect(fill = "grey80", colour = "grey50"))+ggtitle(paste0("NORTH-EASTERN ISLANDS | ",nrow(df3)/2))
}
plot_empty(alldata%>%filter(name == zonelist[55]))
```

Plot Everything
```{r}
library(ggpubr)

p1 = plotrose(alldata%>%filter(name == order[1]))
p2 = plotrose(alldata%>%filter(name == order[2]))
p3 = plotrose(alldata%>%filter(name == order[3]))
p4 = plotrose(alldata%>%filter(name == order[4]))
p5 = plotrose(alldata%>%filter(name == order[5]))
p6 = plotrose(alldata%>%filter(name == order[6]))
p7 = plotrose(alldata%>%filter(name == order[7]))
p8 = plotrose(alldata%>%filter(name == order[8]))
p9 = plotrose(alldata%>%filter(name == order[9]))
p10 = plotrose(alldata%>%filter(name == order[10]))

p11 = plotrose(alldata%>%filter(name == order[11]))
p12 = plotrose(alldata%>%filter(name == order[12]))
p13 = plotrose(alldata%>%filter(name == order[13]))
p14 = plotrose(alldata%>%filter(name == order[14]))
p15 = plotrose(alldata%>%filter(name == order[15]))
p16 = plotrose(alldata%>%filter(name == order[16]))
p17 = plotrose(alldata%>%filter(name == order[17]))
p18 = plotrose(alldata%>%filter(name == order[18]))
p19 = plotrose(alldata%>%filter(name == order[19]))
p20 = plotrose(alldata%>%filter(name == order[20]))

p21 = plotrose(alldata%>%filter(name == order[21]))
p22 = plotrose(alldata%>%filter(name == order[22]))
p23 = plotrose(alldata%>%filter(name == order[23]))
p24 = plotrose(alldata%>%filter(name == order[24]))
p25 = plotrose(alldata%>%filter(name == order[25]))
p26 = plotrose(alldata%>%filter(name == order[26]))

p26_5 = plot_empty(alldata%>%filter(name == order[55]))

p27 = plotrose(alldata%>%filter(name == order[27]))
p28 = plotrose(alldata%>%filter(name == order[28]))
p29 = plotrose(alldata%>%filter(name == order[29]))
p30 = plotrose(alldata%>%filter(name == order[30]))

p31 = plotrose(alldata%>%filter(name == order[31]))
p32 = plotrose(alldata%>%filter(name == order[32]))
p33 = plotrose(alldata%>%filter(name == order[33]))
p34 = plotrose(alldata%>%filter(name == order[34]))
p35 = plotrose(alldata%>%filter(name == order[35]))
p36 = plotrose(alldata%>%filter(name == order[36]))
p37 = plotrose(alldata%>%filter(name == order[37]))
p38 = plotrose(alldata%>%filter(name == order[38]))
p39 = plotrose(alldata%>%filter(name == order[39]))
p40 = plotrose(alldata%>%filter(name == order[40]))

p41 = plotrose(alldata%>%filter(name == order[41]))
p42 = plotrose(alldata%>%filter(name == order[42]))
p43 = plotrose(alldata%>%filter(name == order[43]))
p44 = plotrose(alldata%>%filter(name == order[44]))
p45 = plotrose(alldata%>%filter(name == order[45]))
p46 = plotrose(alldata%>%filter(name == order[46]))
p47 = plotrose(alldata%>%filter(name == order[47]))
p48 = plotrose(alldata%>%filter(name == order[48]))
p49 = plotrose(alldata%>%filter(name == order[49]))
p50 = plotrose(alldata%>%filter(name == order[50]))

p51 = plotrose(alldata%>%filter(name == order[51]))
p52 = plotrose(alldata%>%filter(name == order[52]))
p53 = plotrose(alldata%>%filter(name == order[53]))
p54 = plotrose(alldata%>%filter(name == order[54]))

p56 = plotsg(alldata)
p56s = plotsgs(alldata)

#ggarrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
#          p11,p12,p13,p14,p15,p16,p17,p18,p19,p10,
#          p21,p22,p23,p24,p25,p26,p27,p28, nrow=7, ncol=4, align = "v")

```


```{r}
#GRAPH FILE

g = ggarrange(p26_5, p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,
          p11,p12,p13,p14,p15,p16,p17,p18,p19,p20,
          p21,p22,p23,p24,p25,p26,p27,p28,p29,p30,
          p31,p32,p33,p34,p35,p36,p37,p38,p39,p40,
          p41,p42,p43,p44,p45,p46,p47,p48,p49,p50,
          p51,p52,p53,p54,p56, nrow=7, ncol=8, align = "v")

#------INTERNAL CIRCULATION

tiff(filename="CLC test.tiff", width=30, height=28, units="in",
     pointsize=5, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
  g
dev.off()

```

